Monte Carlo and non-uniform bootstrap

### 2024-07-30 MC_adagrid.Rmd
Correction for bootstrap 1

The goal of this document is to create a large number of Monte Carlo iterations to produce estimators (for the number of trees, the volume of trees and the ratio volume of trees / number of trees), variances of these estimators and confidence intervals. The same elements are also computed for each bootstrap series derived from a smaller number of Monte Carlo iterations. By comparing the two results, we may verify the invalidity of the bootstrap strategy to find the estimation of the variances.

@@

  p <- sum(rep((1/1000)*(1/1000), n))
  BOOT_df <- list() # All local variables
  BOOT_est <- list() # All estimations
  BOOT_var <- list() # Variances
  BOOT_CI <- list() # Confidence Intervals
  for (b in 1:B1) { # One MC iteration at a time
    # Uniform sampling over the whole territory
    df_grid <- sampling_grid(i,c_dim)
    a1 <- df_grid$x
    a2 <- df_grid$y
    a3 <- df_grid$line
    var <- mapply(circle_all, a1, a2)
    df_b <- data.frame(x = a1, y = a2, w = a3, z = t(var)[,1], t = t(var)[,2])
    colnames(df_b) <- c(paste("x.MC", b, sep = ""), paste("y.MC", b, sep = ""), paste("l.MC", b, sep = ""), paste("nb.MC", b, sep = ""), paste("vol.MC", b, sep = ""))
    est_b <- t(data.frame(x = sum(df_b[4] /p), y = sum(df_b[5] /p), z = (sum(df_b[5] /p))/(sum(df_b[4]/p))))

>>>>

The goal of this document is to create a large number of Monte Carlo iterations to produce estimators (for the number of trees, the volume of trees and the ratio volume of trees / number of trees), variances of these estimators and confidence intervals. The same elements are also computed for each bootstrap series derived from a smaller number of Monte Carlo iterations. By comparing the two results, we may verify the (in)validity of the bootstrap strategy to find the estimation of the variances.

@@

  p <- sum(rep((1/1000)*(1/1000), n))
  BOOT_df <- list() # All local variables
  BOOT_est <- list() # All estimations
  BOOT_var <- list() # Variances
  BOOT_CI <- list() # Confidence Intervals
  for (b in 1:B1) { # One MC iteration at a time
    # Uniform sampling over the whole territory
    df_grid <- sampling_grid(i,c_dim)
    a1 <- df_grid$x
    a2 <- df_grid$y
    a3 <- df_grid$line
    var <- mapply(circle_all, a1, a2)
    df_b <- data.frame(x = a1, y = a2, w = a3, z = t(var)[,1], t = t(var)[,2])
    colnames(df_b) <- c(paste("x.MC", b, sep = ""), paste("y.MC", b, sep = ""), paste("l.MC", b, sep = ""), paste("nb.MC", b, sep = ""), paste("vol.MC", b, sep = ""))
    est_b <- t(data.frame(x = (100/99)*sum(df_b[4] /p), y = (100/99)*sum(df_b[5] /p), z = (100/99)*(sum(df_b[5] /p))/(sum(df_b[4]/p))))
